\section{Discussion}
One limitation of our approach is that refactoring assertions about
API secrets out of API tests can result in duplicated testing
code. This might be avoided by using a more complex test design, but
that could reducing the readability of test, making them less useful
as specifications.

We expected to find some interface tests that could not be effectively
refactored to remove API secrets. We did not find any such tests, but
the small scope of our study prevents us from making any conclusions
about the likelyhood of this scenario in practice. 

Another limitation relates to our definition of interface
specification. As an example, a test \texttt{assert add (2, 3) == 5}
only checks that the sum of 2 and 3 is 5. The client may incorrectly
interpret this as saying that the sum of any two numbers is 5, or
even that the sum of any two objects is 5. We conjecture that such
problems could be addressed by adding more tests, or by using
techniques such as concolic testing~\cite{sen05-cute} or random
testing~\cite{quickcheck}. The advantage of our approach is that the
interface and its guarantees are concretely described and
machine-checkable.

Future work: we can use cross-version testing for other things. For
example, library authors don't always choose the most precise version
number. They might issue a major version release that includes no
breaking changes or new features, in order to signal an increased
maturity. In this case a patch release would have been possible, and
in many ways preferable. Clients may not adopt the new version because
they are wary of breaking changes. Our cross-version testing technique
could detect that the new version still supports specification of the
previous version. As a result, clients to adopt the new version more
quickly and with less effort.


\section{Conculsion} 
We have presented a new testing discipline for writing module
interface specifications, and a cross-version testing approach to
detecting Semantic Versioning violations. We built a tool based on our
techniques, and evaluated them using several experiments. Our results
show that our techniques are effective even without interface tests
that adhere that our testing discipline.  Further, there is evidence
that our discipline is natural, in that test suites for mature
libraries may naturally evolve to align with it. Finally, adopting the
discipline does not require too much effort, and can provide even
better results.

